Reading main files and preparing data sets

### 2025-01-20 data-raw/03-preprocessing-main-files.Rmd
inclusion of section for python integration and how to use this package
adding helth-related variables to the 2015 main gss dataset

Read the Main files of the 2015 GSS survey:

@@

```{r filtering-variables-2015}
gss_main_2015 <- gss_m_2015 %>%
  select(PUMFID:DVTDAY)
```

@@

>>>>

Read the Main file of the 2015 GSS survey:

@@

```{r filtering-variables-2015}
gss_main_2015 <- gss_m_2015 %>%
  select(PUMFID:DVTDAY, SLM_01, SRH_110, SRH_115)
```

@@

```{r SLM_01-2015}
values_ordered <- c("10 - Very satisfied","9","8","7","6","5",
                    "4","3","2","1","0 - Very dissatisfied",
                    "Valid skip", 
                    "Don’t know", 
                    "Refusal", 
                    "Not stated")

gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SLM_01: Using a scale of 0 to 10 where 0 means "Very dissatisfied" and 10 means "Very satisfied",how do you feel about your life as a whole right now? 
    SLM_01 = 
      case_when(SLM_01 == 0 ~ "0 - Very dissatisfied",
                SLM_01 == 1 ~ "1",
                     SLM_01 == 2 ~ "2",
                     SLM_01 == 3 ~ "3",
                     SLM_01 == 4 ~ "4",
                     SLM_01 == 5 ~ "5",
                     SLM_01 == 6 ~ "6",
                     SLM_01 == 7 ~ "7",
                     SLM_01 == 8 ~ "8",
                     SLM_01 == 9 ~ "9",
                     SLM_01 == 10 ~ "10 - Very satisfied",
                     SLM_01 == 96 ~ "Valid skip",
                     SLM_01 == 97 ~ "Don’t know",
                     SLM_01 == 98 ~ "Refusal",
                     SLM_01 == 99 ~ "Not stated"),
    SLM_01 = factor(SLM_01, levels = rev(values_ordered), ordered = TRUE))

summary(gss_main_2015$SLM_01)
```

```{r SRH_110-2015}
values_ordered <- c("Excellent","Very good","Good",
                    "Fair","Poor",
                    "Valid skip", 
                    "Don’t know", 
                    "Refusal", 
                    "Not stated")

gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SRH_110: In general, would you say your health is...? 
    SRH_110 = 
      case_when(SRH_110 == 1 ~ "Excellent",
                     SRH_110 == 2 ~ "Very good",
                     SRH_110 == 3 ~ "Good",
                     SRH_110 == 4 ~ "Fair",
                     SRH_110 == 5 ~ "Poor",
                     SRH_110 == 6 ~ "Valid skip",
                     SRH_110 == 7 ~ "Don’t know",
                     SRH_110 == 8 ~ "Refusal",
                     SRH_110 == 9 ~ "Not stated"),
    SRH_110 = factor(SRH_110, levels = rev(values_ordered), ordered = TRUE))

summary(gss_main_2015$SRH_110)
```

```{r SRH_115-2015}
values_ordered <- c("Excellent","Very good","Good",
                    "Fair","Poor",
                    "Valid skip", 
                    "Don’t know", 
                    "Refusal", 
                    "Not stated")

gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SRH_115: In general, would you say your mental health is...?
    SRH_115 = 
      case_when(SRH_115 == 1 ~ "Excellent",
                     SRH_115 == 2 ~ "Very good",
                     SRH_115 == 3 ~ "Good",
                     SRH_115 == 4 ~ "Fair",
                     SRH_115 == 5 ~ "Poor",
                     SRH_115 == 6 ~ "Valid skip",
                     SRH_115 == 7 ~ "Don’t know",
                     SRH_115 == 8 ~ "Refusal",
                     SRH_115 == 9 ~ "Not stated"),
    SRH_115 = factor(SRH_115, levels = rev(values_ordered), ordered = TRUE))

summary(gss_main_2015$SRH_115)
```
